---
title: "SDS315_HW3"
author: "William Zuo"
date: "2025-02-02"
output:
  html_document:
    toc: true
    toc_float: true
  pdf_document:
    toc: true
---

```{r global_options, include=FALSE}
#needed packages:
library(tidyverse)
library(mosaic)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
```

# **Introduction**

My name is William Zuo and my EID is wcz82. This is where my results and solutions are contained. Here is the link to my GitHub repository containing my R code for this assignment: https://github.com/black-bird5/SDS315_HW3. 

# **Problem 1**

```{r, echo=FALSE}
gas <- read.csv('GasPrices.csv')
```

### **Theory A**

```{r, echo=FALSE}
boot_gas_a = do(10000) * diffmean(Price ~ Competitors, data = mosaic::resample(gas))
confint(boot_gas_a, level = 0.95)
```

Claim: Gas stations charge more if they lack direct competition in sight.

Evidence: The difference in mean prices between gas stations with direct competitors in sight and those who don't is between -0.056 dollars and 0.008 dollars, with 95% confidence. Since 0 is contained within our confidence interval, this theory is unsupported by the data. 

Conclusion: At a 5% significance level, there is no statistically significant difference between the price of gas at gas stations that have other gas stations in sight compared to those that do not. 

### **Theory B**

```{r, echo=FALSE}
boot_gas_b <- do(10000) * {
  gas_resampled <- resample(gas)
  cor(gas_resampled$Income, gas_resampled$Price)  
}

confint(boot_gas_b, level = 0.95)
```

Claim: The richer the area, the higher the gas prices.

Evidence: The correlation between gas station prices and the median household income of an area is between 0.193 and 0.568, with 95% confidence. Since 0 is not contained within our confidence interval, this theory is supported by the data, and we can say, with 95% confidence, there is a medium level of correlation between gas prices and the median household income of the ZIP code where the gas station is located. 

Conclusion: At a 5% significance level, there is a statistically significant correlation between the price of gas and the median household income of the ZIP code where the gas station is located. 

### **Theory C**

```{r, echo=FALSE}
boot_gas_c = do(10000) * diffmean(Price ~ Stoplight, data = mosaic::resample(gas))
confint(boot_gas_c, level = 0.95)
```

Claim: Gas stations at stoplights charge more.

Evidence: The difference in mean prices between gas stations at stoplights and those not at stoplights is between -0.038 dollars and 0.03 dollars with 95% confidence. Since 0 is contained within our confidence interval, this theory is unsupported by the data. 

Conclusion: At a 5% significance level, there is no statistically significant difference between the price of gas at gas stations that have a stoplight in front of them compared to those that do not. 

### **Theory D**

```{r, echo=FALSE}
boot_gas_d = do(10000) * diffmean(Price ~ Highway, data = mosaic::resample(gas))
confint(boot_gas_d, level = 0.95)
```

Claim: Gas stations with direct highway access charge more.

Evidence: The difference in mean prices between gas stations with direct highway access and those without is between 0.008 dollars and 0.081 dollars with 95% confidence. Since 0 is not contained within our confidence interval, this theory is supported by the data, and we can say, with 95% confidence, gas stations with direct highway access change slightly more than gas stations without. 

Conclusion: At a 5% significance level, there is a statistically significant difference between the price of gas at gas stations that are accessible from either a highway or a highway access road compared to those that do not. 

### **Theory E**

```{r, echo=FALSE}
gas <- mutate(gas, isShell = (gas$Brand == "Shell"))

boot_gas_e = do(10000) * diffmean(Price ~ isShell, data = mosaic::resample(gas))
confint(boot_gas_e, level = 0.95)
```

Claim: Shell charges more than all other non-Shell brands.

Evidence: The difference in mean prices between Shell gas stations and non-Shell gas stations is between -0.01 dollars and 0.065 dollars with 95% confidence. Since 0 is contained within our confidence interval, this theory is unsupported by the data. 

Conclusion: At a 5% significance level, there is no statistically significant difference between the price of gas at Shell gas stations compared to other gas stations brands. 

# **Problem 2**

```{r, echo=FALSE}
cars <- read.csv('sclass.csv')
```

### **Part A**

```{r, echo=FALSE}
cars_filtered1 <- cars[cars$year == 2011 & cars$trim == "63 AMG",]

boot_mileage = do(10000) * mean(~mileage, data = mosaic::resample(cars_filtered1))
confint(boot_mileage, level = 0.95)
```

The average mileage of all 2011 S-Class 63 AMGs is between 26216 and 31833 miles, with 95% confidence. 

### **Part B**

```{r, echo=FALSE}
cars_filtered2 <- cars[cars$year == 2014 & cars$trim == "550",]
cars_filtered2 <- mutate(cars_filtered2, isBlack = (cars_filtered2$color == "Black"))

boot_isBlack = do(10000) * prop(~isBlack == TRUE, data = mosaic::resample(cars_filtered2))
confint(boot_isBlack, level = 0.95)
```

The proportion of all 2014 S-Class 550s painted black is between 0.416 and 0.453, with 95% confidence. 

# **Problem 3**

```{r, echo=FALSE}
nbc <- read.csv('nbc_pilotsurvey.csv')
```

### **Part A**

```{r, echo=FALSE}
ed <- nbc[nbc$Show == "Living with Ed",]
earl <- nbc[nbc$Show == "My Name is Earl",]
ee_combined <- rbind(ed, earl)

boot_happy = do(10000) * diffmean(Q1_Happy ~ Show, data = mosaic::resample(ee_combined))
confint(boot_happy, level = 0.95)
```

Question:  Is there evidence that either "Living with Ed" or "My Name is Earl" consistently produced a higher mean "Q1_Happy" response among viewers?

Approach: First, I created a new dataset that only contains the shows, "Living with Ed" and "My Name is Earl." Then, I created 10000 bootstrap samples from the new dataset. Finally, I computed a 95% bootstrap confidence interval for the difference in mean response scores to "Q1_Happy" between shows.

Results: The difference in responses to "Q1_Happy" between viewers of "Living with Ed" and viewers of "My Name is Earl" is between -0.391 and 0.101, with 95% confidence. Since 0 is contained within our confidence interval, there is no evidence that either "Living with Ed" or "My Name is Earl" consistently produced a higher mean "Q1_Happy" response among viewers.

Conclusion: At a 5% significance level, there is no statistically significant difference between the response scores to "Q1_Happy" between viewers of "Living with Ed" and viewers of "My Name is Earl."

### **Part B**

```{r, echo=FALSE}
loser <- nbc[nbc$Show == "The Biggest Loser",]
apprentice <- nbc[nbc$Show == "The Apprentice: Los Angeles",]
la_combined <- rbind(loser, apprentice)

boot_annoyed = do(10000) * diffmean(Q1_Annoyed ~ Show, data = mosaic::resample(la_combined))
confint(boot_annoyed, level = 0.95)
```

Question: Is there evidence that either "The Biggest Loser" or "The Apprentice: Los Angeles" consistently produced a higher mean "Q1_Annoyed" response among viewers?

Approach: First, I created a new dataset that only contains the shows, "The Biggest Loser" and "The Apprentice: Los Angeles." Then, I created 10000 bootstrap samples from the new dataset. Finally, I computed a 95% bootstrap confidence interval for the difference in mean response scores to "Q1_Annoyed" between shows.

Results: The difference in responses to "Q1_Annoyed" between viewers of "The Biggest Loser" and viewers of "The Apprentice: Los Angeles" is between -0.521 and -0.019, with 95% confidence. Since 0 is not contained within our confidence interval, there is evidence that either "The Biggest Loser" or "The Apprentice: Los Angeles" consistently produced a higher mean "Q1_Annoyed" response among viewers.

Conclusion: At a 5% significance level, there is a statistically significant difference between the response scores to "Q1_Annoyed" between viewers of "The Biggest Loser" and viewers of "The Apprentice: Los Angeles."

### **Part C**

```{r, echo=FALSE}
stars <- nbc[nbc$Show == "Dancing with the Stars",]

boot_confused = do(10000) * prop(~Q2_Confusing >= 4, data = mosaic::resample(stars))
confint(boot_confused, level = 0.95)
```

Question: What proportion of American TV watchers would we expect to give a response of 4 or greater to the “Q2_Confusing” question for the show, "Dancing with the Stars"?

Approach: First, I created a new dataset that only contains the show, "Dancing with the Stars." Then, I created 10000 bootstrap samples from the new dataset. Finally, I computed a 95% bootstrap confidence interval for the proportion of viewers who responded with a score of 4 or more to the "Q2_Confusing" question.

Results: The proportion of American TV watchers we would expect to give a response of 4 or more to the “Q2_Confusing” question is between 0.039 and 0.116, with 95% confidence. 

Conclusion: At a 5% significance level, there is a statistically significant proportion of viewers who gave a response of 4 or more to the "Q2_Confusing" question for the show "Dancing with the Stars."


# **Problem 4**

```{r, echo=FALSE}
ebay <- read.csv('ebay.csv')
```

```{r, echo=FALSE}
ebay <- mutate(ebay, rev_ratio = rev_after/rev_before)

boot_ebay = do(10000) * diffmean(rev_ratio ~ adwords_pause, data = mosaic::resample(ebay))
confint(boot_ebay, level = 0.95)
```

Question: Is there evidence that DMAs with paid search results have a higher revenue ratio compared to to DMAs without them? 

Approach: First, I created a new variable within the original dataset, the revenue ratio, which is the ratio of revenue after the experiment started to the revenue before it started. Then, I created 10000 bootstrap samples from the new dataset. Finally, I computed a 95% bootstrap confidence interval for the difference in mean revenue ratios between DMAs with paid search results and those without them. 

Results: The difference in the mean revenue ratio between DMAs with paid search results and those without them is between -0.09 dollars and -0.014 dollars, with 95% confidence. Since 0 is not contained within our confidence interval, there is evidence that DMAs with paid search results have a higher revenue ratio compared to to DMAs without them.

Conclusion: At a 5% significance level, there is a statistically significant difference between the revenue ratio of DMAs with paid search results and those without them. This means that we are 95% confident that EBay's paid search advertising on Google was driving extra revenue.
